Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v1.0)} \underline{Drafting Committee: DC90 (\today)}

### 2011-06-14 background_and_systematic.tex
Fixed typos and removed reference to Guidal.

\section{Background Corrections and Systematic Uncertainties}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, 
shifts in the missing-mass distributions and various detector and binning
effects determined in \red{the same manner as in} Refs.~\cite{Air08,Air09}.

The contribution to the uncertainties on the amplitude measurements
\red{arising} from background in the data from neutral meson
production \red{is predominantly due to the misidentification of
  $\pi^0$ mesons}. The procedure is described in detail in
Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of
the measurements addressed here are given in
Table~\ref{table_systematic_contributions_0607} for the amplitudes
extracted in a single bin in the H{\sc ermes} kinematic
region. \red{Each  measurement in the $-t$, $x_{\textrm{B}}$ and
  $Q^{2}$ projections has this uncertainty included as part of the
  total systematic uncertainty.}

\red{The} contribution to the systematic uncertainties from the relative shift of the
missing-mass distributions \red{arises due to} shifts in the
distributions \red{between} electron and positron data~\cite{Zei09,Bur10}. The
missing-mass distribution is also adjusted for each calorimeter calibration period of data
collected in 2007 to account for \red{an} observed time dependence. One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty.

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing
effects due to detector resolution and radiative processes, and
\red{the} finite bin width \red{of the} $-t$, $x_{\textrm{B}}$ and $Q^{2}$ \red{projections}. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. An event
generator based on the GPD model described in Ref.~\cite{Guz06} was
used for the simulation because it describes the data well and is
consistent with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted
from these simulated events using the same analysis procedure used to
extract amplitudes from experimental data. In each kinematic bin, the
systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.

The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background correction, missing-mass shift, and detector effect
uncertainties added in quadrature.  The 1996-2005 sample also has a
systematic uncertainty from misalignment of the
spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample \red{due to improved
  surveying measurements of the spectrometer~\cite{Bur10}. The contribution from
each uncertainty to each amplitude extracted in a single kinematic bin
from the 2006-07 data  is summarised in Table
\ref{table_systematic_contributions_0607}.}

The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
which is present in the beam-helicity amplitudes and is quoted as an
independent scale uncertainty. \red{The systematic uncertainty quoted for each
  amplitude measurement therefore does not include any uncertainty due to the
  measurement of the beam polarisation.}

The data sample in the exclusive region contains events involving both
production of real photons in which the proton remains intact and
events involving the excitation of the target proton to a $\Delta^+$
resonant state. The recoiling proton is not detected and
  the calorimeter resolution does not allow separation of the latter events from rest of the data sample.
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation from Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``Assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform this estimation is described in detail in
Ref.~\cite{Air08}.

>>>>

\section{Background Corrections and Systematic Uncertainties for the
  2006-2007 Data}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, 
shifts in the missing-mass distributions and various detector and binning
effects determined in \red{the same manner as in} Refs.~\cite{Air08,Air09}.

The contribution to the uncertainties on the amplitude measurements
\red{arising} from background in the data from neutral meson
production \red{is predominantly due to the misidentification of
  $\pi^0$ mesons}. The procedure \red{for estimating the corresponding
uncertainty on the measured amplitude values} is described in detail in
Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of
the measurements addressed here are given in
Table~\ref{table_systematic_contributions_0607} for the amplitudes
extracted in a single bin in the H{\sc ermes} kinematic
region. \red{Each  measurement in the $-t$, $x_{\textrm{B}}$ and
  $Q^{2}$ projections has this uncertainty, which is estimated at the
  centre of the relevant kinematic bin, included as part of the
  total systematic uncertainty.}

\red{The} contribution to the systematic uncertainties\red{of the
  measured amplitudes} from the relative shift of the
missing-mass distributions \red{arises due to} shifts in the
distributions \red{between} electron and positron data~\cite{Zei09,Bur10}. The
missing-mass distribution is also adjusted for each calorimeter calibration period of data
collected in 2007 to account for \red{an} observed time dependence. One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty.

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing
effects due to detector resolution and radiative processes \red{during
  detection, (e.g. of the photon in the calorimeter \cite{Bur10})}, and
\red{the} finite bin width \red{of the} $-t$, $x_{\textrm{B}}$ and $Q^{2}$ \red{projections}. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. An event
generator based on the GPD model described in Ref.~\cite{Guz06} was
used for the simulation because it describes the data well and is
consistent with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted
from these simulated events using the same analysis procedure used to
extract amplitudes from experimental data. In each kinematic bin, the
systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
\red{input} from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.

The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin \red{by adding in quadrature the
  uncertainties arising from the background correction, the
  missing-mass shifts, and the detector effects}.  The 1996-2005 sample also has a
systematic uncertainty from misalignment of the
spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample \red{due to improved
  surveying measurements~\cite{Bur10}. The contribution from
each uncertainty to each amplitude extracted in a single kinematic bin
from the 2006-2007 data  is summarised in Table
\ref{table_systematic_contributions_0607}.}

The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
which is present in the beam-helicity amplitudes and is quoted as an
independent scale uncertainty. \red{The systematic uncertainty shown for each
  amplitude measurement therefore does not include any uncertainty due to the
  measurement of the beam polarisation.}

The data sample in the exclusive region contains events involving both
production of real photons in which the proton remains intact and
events involving the excitation of the target proton to a $\Delta^+$
resonant state \red{(``associated production'')}. The recoiling proton is not detected and
  the calorimeter resolution does not allow separation of the latter events from rest of the data sample.
No systematic uncertainty is assigned for the contribution from these
events; they are treated as part of the signal. A Monte Carlo
calculation based on the parameterisation from Ref.~\cite{Bra76} is
used to estimate the contribution to the event sample from resonant
production in each kinematic bin. The results, \red{called the associated fractions} and labelled ``Assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform this estimation is described in detail in
Ref.~\cite{Air08}.

### 2011-06-14 experiment_and_data.tex
Fixed typos and removed reference to Guidal.

\section{Experiment and Data Selection}
The data were collected in 2006 and 2007 with the H{\sc ermes}
spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the \red{H\sc{era}} lepton storage ring at \red{D\sc{esy}}. The integrated
luminosities of the electron and positron data samples\red{,} respectively\red{,} are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is similar to that used in Ref.~\cite{Air09}.
A brief summary of this procedure is outlined in the following; consult
Refs.~\cite{Zei09,Bur10} for more details.

@@

The expectation value of the experimental yield $N$ is parameterised as
\begin{equation}
 \langle N(e_{\ell},P_{\ell},\phi)\rangle =
\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{\textrm{UU}}
(\phi)\times
[1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)+e_{\ell}\mathcal{A}_{\textrm{C}}
(\phi)],
\end{equation}
where \red{$P_\ell$ is the beam polarisation, }$\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
efficiency and d$\sigma_{\textrm{UU}}$ denotes the
cross section for an unpolarised target integrated over both beam charges and
beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$,
$\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$ and
$\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
$\phi$ as
\begin{equation}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,I}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,I}}^{\cos(n\phi)}\cos(n\phi), 
\label{alui_asym}
\end{equation}
\begin{equation}
 \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq 
A_{\textrm{LU,DVCS}}^{\sin\phi}\sin\phi 
+ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
\label{aludvcs_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{C}}(\phi) \simeq \sum^{3}_{n=0}
A_{\textrm{C}}^{\cos(n\phi)}\cos(n\phi) 
+ A_{\textrm{C}}^{\sin\phi}\sin\phi,
\label{ac_asym}
\end{equation}
where the approximation is due to the truncation of the infinite
Fourier series \red{that would describe the fitted distribution
  perfectly}. Only the $\sin(n\phi)$ terms of the
$\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
$\mathcal{A}_{\textrm{C}}$ asymmetry are physically motivated. The other terms
are included as both a consistency check for \red{any off-phase}
extraneous harmonics \red{in the data} and as a test of the
normalisation of the fit. These terms are expected to be
\red{consistent with zero}.

@@

The asymmetry amplitudes $A_{\textrm{LU,I/DVCS}}^{\sin(n\phi)}$ and
$A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
coefficients $s_{n}^{W}$ and $c_{n}^{I}$ from the interference and
DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
may also be affected by the lepton propagators and the other
$\phi$-dependent terms in the denominators in
Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier
coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
combination of complex Compton Form Factors (CFF). A CFF is a convolution of a GPD with a hard scattering kernel. Contributions of GPDs to the cross section may be relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD. The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross section in which the amplitude appears. Leading twist is twist-2. Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is suppressed by $\mathcal{O}(1/Q^{n-2})$. Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and levels of suppression.

At H{\sc ermes} kinematic conditions, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes, for an unpolarised target, are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{center}
\begin{equation}
 s_{1,\textrm{unp}}^{\textrm{I}} \approx 8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:s1}
\end{equation}
\end{center}
\begin{center}
\begin{equation}
 c_{1,\textrm{unp}}^{\textrm{I}} \approx 8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:c1}
\end{equation}
\end{center}
where the kinematic factor $k \propto \sqrt{-t}/Q$ originates from the BH
propagators. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{\red{-}t}{4M^2}$ are of order 0.1), the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} \red{(in first approximation)} with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, in this approximation, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$. \red{Therefore}, $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes enter the cross section at a higher
twist level (see Table~\ref{tab_amplitudes}).

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. This
$\mathcal{C}$-function receives contributions from both the BH and DVCS
processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
where $\alpha_{\textrm{S}}$ is the\red{strong} constant.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist Level & Relative Suppression   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2&\red{kinematic}
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression
 \red{relative to the leading amplitudes at H\sc{ermes} kinematic conditions}~\cite{Bel02b}.}
\label{tab_amplitudes}
\end{center}
\end{table}

>>>>

\section{Experiment and Data Selection}
The \red{new} data \red{presented in this work were} collected in 2006 and 2007 with the H{\sc ermes}
spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the \red{H\sc{era}} lepton storage ring at \red{D\sc{esy}}. The integrated
luminosities of the electron and positron data samples\red{,} respectively\red{,} are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is similar to that used in Ref.~\cite{Air09}.
A brief summary of this procedure is outlined in the following; consult
Refs.~\cite{Zei09,Bur10} for more details.

@@

The expectation value of the experimental yield $N$ is parameterised as
\begin{equation}
 \langle N(e_{\ell},P_{\ell},\phi)\rangle =
\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{\textrm{UU}}
(\phi)\times
[1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)+e_{\ell}\mathcal{A}_{\textrm{C}}
(\phi)],
\end{equation}
where \red{$P_\ell$ is the beam polarisation, }$\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
efficiency and d$\sigma_{\textrm{UU}}$ denotes the
cross section for an unpolarised target integrated over both beam charges and
beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$,
$\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$ and
$\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
$\phi$ as
\begin{equation}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,I}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,I}}^{\cos(n\phi)}\cos(n\phi), 
\label{alui_asym}
\end{equation}
\begin{equation}
 \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq 
A_{\textrm{LU,DVCS}}^{\sin\phi}\sin\phi 
+ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
\label{aludvcs_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{C}}(\phi) \simeq \sum^{3}_{n=0}
A_{\textrm{C}}^{\cos(n\phi)}\cos(n\phi) 
+ A_{\textrm{C}}^{\sin\phi}\sin\phi,
\label{ac_asym}
\end{equation}
where the approximation is due to the truncation of the infinite
Fourier series \red{that would describe the fitted distribution
  perfectly}. Only the $\sin(n\phi)$ terms of the
$\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
$\mathcal{A}_{\textrm{C}}$ asymmetry are physically motivated. The other terms
are included as both a consistency check for \red{any off-phase}
extraneous harmonics \red{in the data} and as a test of the
normalisation of the fit. These terms are expected to be
\red{consistent with zero and are found to be so}.

@@

The asymmetry amplitudes $A_{\textrm{LU,I/DVCS}}^{\sin(n\phi)}$ and
$A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
coefficients $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{I}$ from the interference and
DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
may also be affected by the lepton propagators and the other
$\phi$-dependent terms in the denominators in
Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{V}$ Fourier
coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
combination of complex Compton Form Factors (CFF). A CFF is a convolution of a GPD with a hard scattering kernel. Contributions of GPDs to the cross section may be relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD. The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross section in which the amplitude appears. Leading twist is twist-2. Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is suppressed by $\mathcal{O}(1/Q^{n-2})$. Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.

At H{\sc ermes} kinematic conditions, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes, for an unpolarised target, are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{center}
\begin{equation}
 s_{1,\textrm{unp}}^{\textrm{I}} \approx 8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:s1}
\end{equation}
\end{center}
\begin{center}
\begin{equation}
 c_{1,\textrm{unp}}^{\textrm{I}} \approx 8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:c1}
\end{equation}
\end{center}
where the \red{definition of the} kinematic factor $k$ \red{is found
  in Ref.\cite{Bel02b}}. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{\red{-}t}{4M^2}$ are of order 0.1), the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} \red{(in first approximation)} with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes enter the cross section at a higher
twist level (see Table~\ref{tab_amplitudes}).

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. This
$\mathcal{C}$-function receives contributions from both the BH and DVCS
processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
where $\alpha_{\textrm{S}}$ is the \red{strong coupling} constant.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist Level & Relative Suppression   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2&\red{kinematic}
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression
 \red{relative to the leading amplitudes at H{\sc ermes} kinematic conditions}~\cite{Bel02b}.}
\label{tab_amplitudes}
\end{center}
\end{table}

### 2011-06-14 frame.tex
Fixed typos and removed reference to Guidal.

\abstract{
Beam-helicity and beam-charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the H{\sc ermes} data set of 2006-2007 using a missing-mass event selection technique. The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from the earlier data set of 1996-2005 previously analysed in the same manner by the collaboration. Results from the two data sets are found to be compatible with each other. Combined results from these data sets are extracted and represent the statistically most precise asymmetry amplitude measurements available in the H{\sc ermes} kinematic region.
}
\keywords{lepton-nucleon scattering}

>>>>

\abstract{
Beam-helicity and beam-charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the H{\sc ermes} data set of 2006-2007 using a
missing-mass event selection technique. The beam-charge asymmetry
amplitudes extracted from the new data set are more
\red{statistically} precise than those extracted from the earlier data
set of 1996-2005 previously analysed in the same manner by the
collaboration. Results from the two data sets are found to be
compatible with each other. Combined results from these data sets are
extracted and represent the most \red{statistically} precise asymmetry amplitude measurements available in the H{\sc ermes} kinematic region.
}
\keywords{lepton-nucleon scattering}
